### 2023-04-20 introduction.tex
up

>>>>

\begin{center}
	\begin{figure}
			\hspace{0.75cm}
				\label{air control}
\includegraphics[width=0.85\textwidth]{FigureB}
	\caption{A channel system with three automata and four channels. Leftmost and rightmost automata represents aircrafts attempting to land and staying on stand-by in the air while they haven't received permission to land, while the middle one represent the control tower managing the aircrafts landings so that only one aircraft at a time is allowed for landing.}
	\end{figure}
\end{center}

Consider the channel system in Figure~\ref{air control}. It models a scenario in which two aircrafts wants to land in an airport at the same time. Safety requires that only one aircraft at a time attempt to land. The role of the control tower is to ensure this;
there are two possible choices: aircraft A waits for aircraft B to land
or vice-versa. We want ...

% contrôle de trafic aérien, perturbation dans le planning → Bad (par exemple, trop d’avions qui cherchent à atterir en même temps et qui doivent être mis en stand-by au dessus de l’aéroport?) → Safe (trafic fluide à nouveau). K-résilience important car les avions peuvent pas rester indéfiniment en stand-by (re : le carburant est un réactif limitant)
